Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-25 draft/chicago-spatial-covid-draft.tex
Fixed spelling and reference errors

\section{Results}
\subsection{ODE Model}
We begin by discussing the zero-dimensional model for Chicago.
Data for the progression of the pandemic in Chicago were obtained from the Chicago Data Portal \cite{Chicago_2021}.
The relevant results are given in Figure \ref{ode_results}.
We obtained the optimal ODE model parameters for Chicago from 1,000 optimizations that compared model predictions to jointly the number of cumulative infected and the deceases, as in Equation \ref{eq:obj}.

>>>>

\section{Results}
\subsection{ODE Model}
We begin by discussing the zero-dimensional model for Chicago.
Data for the progression of the pandemic in Chicago were obtained from the Chicago Data Portal \cite{Chicago_2021}.
The relevant results are given in Figure \ref{fig:ode_results}.
We obtained the optimal ODE model parameters for Chicago from 1,000 optimizations that compared model predictions to jointly the number of cumulative infected and the deceased, as in Equation \ref{eq:obj}.
